---
title: "p8105_hw_5_bw2595"
author: "Blair Wigsten"
date: "11/6/2019"
output: html_document
---

```{r}
getwd()
```

# Problem 1: load packages 

```{r}
library(tidyverse)
library(readr)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```

```{r}
replaced_iris = function(x) {
  if(is.numeric(x)) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  } else if (is.character(x)) {
    ifelse(is.na(x), "virginica", x)
  }
}

iris_full = map_df(iris_with_missing, replaced_iris)
iris_full
```



# Problem 2

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
data = tibble(
  observation = list.files(path = "./data")
)
data
```


