---
title: "p8105_hw_5_bw2595"
author: "Blair Wigsten"
date: "11/11/2019"
output: github_document
---

# Problem 1

## Load packages and run code given  

```{r}
library(tidyverse)
library(readr)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```

## Fill in missing character and numeric values, and write a function that takes a vector as an argument
```{r}
replaced_iris = function(x) {
  if(is.numeric(x)) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  } else if (is.character(x)) {
    ifelse(is.na(x), "virginica", x)
  }
}

iris_full = map_df(iris_with_missing, replaced_iris)
iris_full
```
* The resulting function replaces all missing character values with "virginica", and replaces all missing numeric values with the mean of non-missing values. The function is applied to the columns of the missing dataset using a map statement. 


# Problem 2

* 
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

## Start with a dataframe containing all file names
```{r}
data = tibble(
  observation = list.files(path = "./data")
)
data
```
* The "data" set lists all files contained in the zip file. 

## Iterate over file names and read in data for each subject and save the result as a new variable in the dataframe and tidy the resulting dataset
```{r}
data = function(path){
  case_control = read_csv(path)
  case_control
} 

directory = "./data"
study = tibble(
  participant = list.files(path = "./data"),
  files = str_c(directory, "/", participant)) %>%
  mutate(
    weekly_data = map(files, read_csv),
    participant = str_replace(participant, ".csv", "")) %>%
  unnest() %>%
  mutate(
  study_arm = if_else(participant %in% c("con_01", "con_02", "con_03", "con_04", "con_05", "con_06", "con_07", "con_08", "con_09", "con_10"), "control", participant),
  study_arm = if_else(participant %in% c("exp_01", "exp_02", "exp_03", "exp_04", "exp_05", "exp_06", "exp_07", "exp_08", "exp_09", "exp_10"), "experimental", study_arm)) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_", 
    values_to = "result")
study
```

* Using purrr:map, we iterated over file names and read in data for each subject. The resulting dataset, "study" is a tidy dataset with participant origin file, study arm, week number, and observation (results). 

## Make a spaghetti plot showing observations on each subject over time
```{r}
plot = study %>%
  ggplot(aes(x = week, y = result, group = participant, color = study_arm)) +
  geom_line() +
  labs(
    title = "Observations for Each Subject Over Time", 
    x = "Week", 
    y = "Results"
  )
plot
```

* This plot shows the trends in results over time, stratified by study arm (experimental vs. control). Just by looking at the graph, there appears to be a difference in results between the control and experimental groups; control subjects appear to have lower results over time, while experimental subjects appear to have increasing results over the 8 week study period. Further statistical tests would need to be done in order to determine the significance of the apparent difference between study arms. 

# Problem 3

## Set design elements and run linear model to obtain p-values and estimated betas, repeat this for beta1 (effect size) of 1-6

```{r}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {

  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50^0.5))

  ls_fit = lm(y ~ x, data = sim_data)
  
  broom::tidy(ls_fit) %>%
    filter(term == "x")
}

sim_results = rerun(10000, sim_regression()) %>%
  bind_rows()

results = tibble(
  beta1 = c(0, 1, 2, 3, 4, 5, 6)) %>%
  mutate(
    output_list = map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_list, bind_rows)) %>%
  select(-output_list) %>%
  unnest(estimate_dfs)
results
```

## Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis

```{r}
graph1 = results %>%
  mutate(
    significant = cut(p.value, breaks = c(0, 0.05, Inf), labels = c("significant", "not significant"))) %>%
  group_by(beta1, significant) %>%
  summarize(number = n()) %>%
  mutate(
    proportion = number / sum(number),
     as.character(beta1)) %>%
  filter(significant == "significant") %>%
  ggplot(aes(x = beta1, y = proportion)) +
  geom_point() + geom_line(group = 1) +
  labs(
      title = "Power of the Test",
      x = "True Value of Beta1",
      y = "Proportion of Times Null was Rejected")
graph1
```

* As the true value of Beta1 increases (the effect size), the power of the test increases. As beta1 moves from 1 to 4, the increase is drastic, then approaches the asymptote of 1 as the effect size reaches 6. 

## Make a plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis.
```{r}
graph2 = results %>%
  group_by(beta1) %>%
  mutate(
    mean_beta1_estimate = mean(estimate)
  ) %>%
  select(beta1, mean_beta1_estimate) %>%
  ggplot(aes(x = beta1, y = mean_beta1_estimate)) +
  geom_point() +
  labs(
      title = "Average Beta1 vs. True Beta1",
      x = "True Value of Beta1",
      y = "Average Value of Beta1")
graph2
```

* This plot shows the average estimate of beta1 vs. the true value of beta1. Shown here, the average beta1 is very close to the true value of beta1 (shown by a strong linear trend).

## Make a second plot of the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis

```{r}
graph3 = results %>%
  mutate(
    significant = cut(p.value, breaks = c(0, 0.05, Inf), labels = c("significant", "not significant"))) %>%
  filter(significant == "significant") %>%
  group_by(beta1) %>%
  mutate(
    mean_beta1_estimate = mean(estimate)
  ) %>%
  select(beta1, mean_beta1_estimate) %>%
  ggplot(aes(x = beta1, y = mean_beta1_estimate)) +
  geom_point() +
  labs(
      title = "Average Beta1 vs. True Beta1 Among Significant Results",
      x = "True Value of Beta1",
      y = "Average Value of Beta1")
graph3
  
```

* The sample average of estimated beta1 is not approximately equal to the true value of beta1. This is to be expected, as the hypothesis test determines which estimates are significantly different from the true betas. Therefore, by restricting results to significant p-values, we are only plotting points that are statistically significantly different from the true values.


