---
title: "p8105_hw_5_bw2595"
author: "Blair Wigsten"
date: "11/6/2019"
output: html_document
---

```{r}
getwd()
```

# Problem 1: load packages 

```{r}
library(tidyverse)
library(readr)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing
```

```{r}
replaced_iris = function(x) {
  if(is.numeric(x)) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  } else if (is.character(x)) {
    ifelse(is.na(x), "virginica", x)
  }
}

iris_full = map_df(iris_with_missing, replaced_iris)
iris_full
```



# Problem 2

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
data = tibble(
  observation = list.files(path = "./data")
)
data
```


# Problem 3

```{r}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {

  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50^0.5))

  ls_fit = lm(y ~ x, data = sim_data)
  
  broom::tidy(ls_fit) %>%
    filter(term == "x")
}

sim_results = rerun(100, sim_regression()) %>%
  bind_rows()

results = tibble(
  beta1 = c(0, 1, 2, 3, 4, 5, 6)) %>%
  mutate(
    output_list = map(.x = beta1, ~rerun(100, sim_regression(beta1 = .x))),
    estimate_dfs = map(output_list, bind_rows)) %>%
  select(-output_list) %>%
  unnest(estimate_dfs)
results
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power. 

```{r}
graph1 = results %>%
  mutate(
    significant = cut(p.value, breaks = c(0, 0.05, Inf), labels = c("significant", "not significant"))) %>%
  group_by(beta1, significant) %>%
  summarize(number = n()) %>%
  mutate(
    proportion = number / sum(number),
     as.character(beta1)) %>%
  filter(significant == "significant") %>%
  ggplot(aes(x = beta1, y = proportion)) +
  geom_point() + geom_line(group = 1) +
  labs(
      title = "Power of the Test",
      x = "True Value of Beta1",
      y = "Proportion of Times Null was Rejected")
graph1
```

* As the true value of Beta1 increases (the effect size), the power of the test increases. As beta1 moves from 1 to 4, the increase is drastic, then approaches the asymptote of 1 as the effect size reaches 6. 

```{r}
graph2 = results %>%
  group_by(beta1) %>%
  mutate(
    mean_beta1_estimate = mean(estimate)
  ) %>%
  select(beta1, mean_beta1_estimate) %>%
  ggplot(aes(x = beta1, y = mean_beta1_estimate)) +
  geom_point() +
  labs(
      title = "Average Beta1 vs. True Beta1",
      x = "True Value of Beta1",
      y = "Average Value of Beta1")
graph2
```

* This plot shows the average estimate of beta1 vs. the true value of beta1. 

```{r}
graph3 = results %>%
  mutate(
    significant = cut(p.value, breaks = c(0, 0.05, Inf), labels = c("significant", "not significant"))) %>%
  filter(significant == "significant") %>%
  group_by(beta1) %>%
  mutate(
    mean_beta1_estimate = mean(estimate)
  ) %>%
  select(beta1, mean_beta1_estimate) %>%
  ggplot(aes(x = beta1, y = mean_beta1_estimate)) +
  geom_point() +
  labs(
      title = "Average Beta1 vs. True Beta1 Among Significant Results",
      x = "True Value of Beta1",
      y = "Average Value of Beta1")
graph3
  
```

* The sample average of estimated beta1 is not approximately equal to the true value of beta1. This is to be expected, as the hypothesis test determines which estimates are significantly different from the true betas. Therefore, by restricting results to significant p-values, we are only plotting points that are statistically significantly different from the true values.